\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-02-23 paper.tex
Back to IROS template

\documentclass[conference]{IEEEtran}
\usepackage{times}

% numbers option provides compact numerical references in the text. 
\usepackage[numbers]{natbib}

\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{graphs,graphdrawing,arrows}
\usegdlibrary{trees, layered}
\usepackage{booktabs} % For formal tables
\usepackage{multicol}
\usepackage[bookmarks=true]{hyperref}

@@

\title{{\sc underworlds}: Cascading Situation Assessment for Robots
}

\author{Author Names Omitted for Anonymous Review. Paper-ID [add your ID here]}

%\author{\authorblockN{Séverin Lemaignan}
%\authorblockA{Centre for Robotics and Neural Systems\\
%University of Plymouth\\
%Plymouth, United Kingdom\\
%Email: severin.lemaignan@plymouth.ac.uk}
%\and
%\authorblockN{Yoan Sallami, Aurélie Clodic and Rachid Alami}
%\authorblockA{Twentieth Century Fox\\
%Springfield, USA\\
%Email: homer@thesimpsons.com}
%\and
%\authorblockN{James Kirk\\ and Montgomery Scott}
%\authorblockA{Starfleet Academy\\
%San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212\\
%Fax: (888) 555--1212}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle

@@

\IEEEpeerreviewmaketitle

@@

\uwds is a distributed and lightweight open-source
%framework \footnote{\url{https://github.com/severin-lemaignan/underworlds}} that
framework \footnote{[GitHub URL hidden for blind review]} that
enables robot programmers to build and refine spatial and temporal
models of the environment surrounding a robot in real-time. \uwds makes it possible to share
these world models amongst the software components running on the robot.
Additionally, \uwds enables users to represent and manipulate
\emph{multiple alternatives} to the current, perceived world model in a distributed manner. For
instance, the world with some objects filtered out; the world `viewed' from the
perspective of another agent; a hypothetical world resulting from the simulated
application of a plan, etc.

@@

%\uwds has been used within the European MuMMER project
\uwds has been used within the [hidden for blind review] project
in order to conceptualise and visualise the spatial relations and visibility of
the physical objects that participants interact with.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{l2tor}
    %\caption{Schema of the \uwds architecture used in the MuMMER project. }
    \caption{TODO LAAS update archi -- Schema of the \uwds architecture used in the [hidden for blind review] project. }
    \label{fig|mummerarchitecture}
\end{figure}

@@

%This work has been supported by the EU H2020 Marie Sk\l odowska-Curie Actions
%project DoRoThy (grant 657227) and the EU H2020 L2TOR project (grant 688014).

%The authors also acknowledge the contribution of the HRI lab of LAAS-CNRS (where this
%work debuted), and in particular, the influential ideas of Rachid Alami.

[Hidden for blind review]

\bibliographystyle{plainnat}
\bibliography{bibliography}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

\usepackage[utf8x]{inputenc}
\usepackage{graphicx}

\usepackage{tikz}
\usetikzlibrary{graphs,graphdrawing,arrows}
\usegdlibrary{trees, layered}
\usepackage{booktabs} % For formal tables
\usepackage{multicol}
\usepackage[bookmarks=true]{hyperref}

@@

\title{\LARGE \bf
{\sc underworlds}: Cascading Situation Assessment for Robots
}

\author{Séverin Lemaignan$^{1}$, Yoan Sallami$^{2}$, Christopher Wallbridge$^{1}$, Aurélie Clodic$^{2}$ and Rachid Alami$^{2}$%
\thanks{$^{1}$Authors are with Centre for Robotics and Neural Systems,
        Plymouth University, Plymouth PL48AA, United Kingdom
        {\tt\small firstname.surname@plymouth.ac.uk},
	$^{2}$Authors are with CNRS LAAS,
        Toulouse, France
        {\tt\small firstname.surname@laas.fr}}%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle
\thispagestyle{empty}
\pagestyle{empty}

@@

@@

\uwds is a distributed and lightweight open-source
framework \footnote{\url{https://github.com/underworlds-robot/underworlds}} that
enables robot programmers to build and refine spatial and temporal
models of the environment surrounding a robot in real-time. \uwds makes it possible to share
these world models amongst the software components running on the robot.
Additionally, \uwds enables users to represent and manipulate
\emph{multiple alternatives} to the current, perceived world model in a distributed manner. For
instance, the world with some objects filtered out; the world `viewed' from the
perspective of another agent; a hypothetical world resulting from the simulated
application of a plan, etc.

@@

\uwds has been used within the European MuMMER project
in order to conceptualise and visualise the spatial relations and visibility of
the physical objects that participants interact with.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{l2tor}
    \caption{TODO LAAS update archi -- Schema of the \uwds architecture used in
    the MuMMER project. }
    \label{fig|mummerarchitecture}
\end{figure}

@@

This work has been supported by the EU H2020 Marie Sk\l odowska-Curie Actions
project DoRoThy (grant 657227),  the EU H2020 MuMMER project (grant TODO LAAS)
and the EU H2020 L2TOR project (grant 688014).

\bibliographystyle{IEEEtran}
\bibliography{bibliography}
